\input{src/first-page/sidebar}

\makefrontsidebar

\cvsection{Education}
    \cvsubsection{Study}
    \begin{cvtable}[1.5]
    	\cvitem{2016 -- 2020}{Computer Systems Engineering}{Instituto Politécnico Nacional}
    		{Studies with strong focus on Logic and Mathematics, with also knowledge about Computer's architecture, Nets, Software Engineering etc. Not finished because of work.
    		}
    \end{cvtable}
    
    \cvsubsection{Certifications}
    \begin{cvtable}[1.5]
    	\cvitem
    	    {2021}
    	    {Associate Cloud Engineer}{Google Cloud Platform}
    		{
    		    Certified about Cloud Knowledge 
    		    \href
    		        {https://www.credential.net/6bb2851b-bfcb-49fc-a891-5f6ea8aef2fe}
    		        {(Link to Certificate here)}
    		}
    \end{cvtable}

\cvsection{Working Experience}
\begin{cvtable}[3]
        \cvitem{May 2023 -- Present}{Cloud Engineer}{Inetum / BBVA}
            {
            Worked with the IA team within BBVA. Designed GCP architecture of a data Ingestion and Processing solution. Managed connections with internal systems, Cloud Functions, workflows, AppEngine, Database, Cloud Build and Jenkinsfiles. Usage of Terraform and Terragrunt for infra. Refactored and built python and JS functions. Worked on frontend with Vue.
	    }
        
        \cvitem{Jun 2022 -- May 2023}{Cloud Engineer}{Praxis / Gentera}
            {
            Worked within Gentera's Cloud Architecture Team. Managed architecture docs and policies. Used GKE and Jenkins. Worked with Google Workflows, Firestore, Python and Java Spring Boot. Made docs sites with Vuepress and Docusaurus, and connected a Teams chatbot with project data to resolve FAQs. Used bash and python scripting for automate data gathering about unused repos and projects. Started my usage of Terraform.
	    }

	\cvitem{Oct 2020 -- Jun 2022}{Full Stack/Cloud Developer}{Mediaagility}{
	    Maintained and enhanced a platform for easy chatbot management of MediaAgility. Worked with Laravel/Lumen. Built projects with GCP technologies. Consumed several Google API’s and services (mainly Serverless, Container related, Data Storage services and DialogFlow, Networking, Compute Engine). Refactored services using SOLID and the basics of Hexagonal Architecture. Added a pipeline for manage private packages with Gitlab CI/CD. Moved monoliths to microservices and libraries. Communication with American clients. Worked with telephony in a Asterisk/Issabel/DialogFlow integration. Worked with Jenkins and DataDog.
	    }
	\cvitem{May 2020 -- Aug 2021}{Freelancer/Co-Founder}{MexaStack}{
	    Deal with clients and take of requirements. Created Gitlab CI pipelines. Leaded a small frontend team. Planned activities for my team. Taught to my team partners. Made deployments and a lot of front-end programming. Used Vue, CSS, Quasar/ElectronJS, Django Rest Framework and Docker. Several projects completed.
	    }
	\cvitem{Oct 2019 -- Apr 2020}{Full-Stack Developer}{G214 Soluciones de Información}{
        Project for CFE CDMX. Worked maintaining and expanding a web platworm built in MySQL, PHP and JQuery. Usage of Docker-compose. Managed servers and made shell scripting
        }
	\cvitem{June 2019 -- Sep 2019}{Data Science Intern}{Konfío}{
    	Done Software Engineering stuff. Worked with AWS serverless solutions. Migrated codebase from PHP / Zend framework / Eloquent ORM to Flask and SqlAlchemy (Python). Worked with Jenkins pipelines.
        Learned about Docker and Data Science python tools (Pandas, Numpy, Matplotlib, scipy). Finished because I still wasn't good enough at Probability/Statistics.
        }
	%\cvitem{Apr 2019 -- May 2019}{Freelancer/Maintainer}{EDKOR}{
        %Made maintenance to a platform for teachers, built in Laravel. I was testing, correcting platform errors and notifying to developer’s team about errors, and how they was corrected.
        %}
\end{cvtable}

\newpage
