% Importing declared sidebar
\input{src/second-page/sidebar}

\makebacksidebar

\begin{cvtable}[3]
    \cvitem{Sep 2018 -- March 2019}{Full-Stack Scholar}{The Member-Cheap Company}{
        Worked with backend on PHP, using MySQL and Sqlite. Backup and synchronization of databases.
        Made manual testing. Made reports and graphing, analyzing logs and client’s data.
        }

    \cvitem{Jan 2018 -- Apr 2018}{Full-Stack Scholar}{InmofinquesMX}{
        	Created a system for employee, selling and supplies control within a fast food franchise. Frequent meetings and deal with the client. I organized a little team (2 people) and the system's architecture.
            }
\end{cvtable}

\cvsection{Awards}
\begin{cvtable}
	\cvitem{2014}{Winner of silver medal in the “Olimpiada Mexicana de Informática” (OMI), at statewide (Estado de México).}{OMI}{}
\end{cvtable}

\cvsection{Skills}

Although my main technologies are described on the \textbf{left sidebar}, there's a bunch of another things I know

\cvsubsection{Also know (Technologies)}
\begin{cvtable}
	\cvitemshort{OS's}{Mac, Windows and Linux}
	\cvitemshort{JavaScript}{Quasar Framework, Mocha}
	\cvitemshort{Python}{Flask, SqlAlchemy}
	\cvitemshort{CSS}{Bootstrap, Bulma, Materialize}
	\cvitemshort{Google Cloud}{Compute Engine, BigQuery,
	    Cloud Storage, Cloud SQL, IAM, AppEngine, Firebase, Dialogflow, Logging, Firebase, Workflows, GKE, Cloud Functions, Looker Studio, AppScript, Cloud Run, Secrets
	    }
	\cvitemshort{CI}{Gitlab CI}
	\cvitemshort{AWS}{S3, Lambdas, Lightsail}
	\cvitemshort{Management}{Trello, Clickup}
	\cvitemshort{Others}{Shell Scripting}
\end{cvtable}

\cvsubsection{Knowledge/Concepts}
\begin{cvtable}

    \cvitemshort{Architecture}{Clean code, MVC, CI/CD concepts,
        POO, SOLID. \\
        Currently learning Design Patterns, DDD, Hexagonal Architecture and improving my Data Structures
        }
	\cvitemshort{Social}{Deal with client}
	\cvitemshort{Management}{Leadership, Tasks assignment,
	    basic knowledge of Scrum
	    }
\end{cvtable}

\cvsection{Extra-Curricular Activities}
\begin{cvtable}
	\cvitemshort{Sports}{ I do Parkour and Boxing. Learning to be a Boxing Trainer}
	\cvitemshort{Music}{Currently on a musical group. A "Tuna"}
	\cvitemshort{Education}{Enthusiast of hackathons and competitive programming}
\end{cvtable} \\

\cvsection{Next steps}

\begin{itemize}
    \item Contribute to the community, either by doing packages and Documentation or by giving talks and teaching into my own community / YouTube channel.
    \item Implement what I'm learning in my nearest projects, like TDD, Typescript, and some Continuous Integration tools for automation.
\end{itemize}


\cvsignature  \watermark.
